\emph{MixFishSim}: highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2019-06-25 write_up/mixfishsim_ecolmod.tex
Text updates and reworking plots

@@

We simulate 50 years of fishing and use the results from the fisheries catch to
draw inference on the underlying population structures. We compare this
inference to i) a simulated fixed-site sampling design commonly used for
fisheries monitoring purposes, and ii) the true underlying population
structures input to the simulation. We use the results to establish the
potential and limitations of fishery-dependent data in providing a robust
picture of spatiotemporal distributions. Finally, we simulate an area closure
based on areas defined from the known ("real-population") distribution,
commercial catch data and survey data at different temporal and spatial
resolutions and assess their effectiveness on reducing catches of a fish
population. \\

@@

Fishers exploit a variety of fish populations that are heterogeneously
distributed in space and time with varying knowledge of species distributions
using species non-selective fishing gear. \added[id=PD]{In doing so} fisheries
\deleted[id=PD]{that}catch an assemblage of species
\added[id=PD]{and}\deleted{, known as mixed fisheries} \replaced[id=JJ]{may}{,
	when managed by single-species quotas can end up}
discard\deleted[id=JJ]{ing} over-quota catch \added[id=JJ]{when managed by
	single species quotas and fishers exhaust or more quota, may} lead to
overexploitation of fish populations \added[id=JJ]{\citep{Ulrich2011a,
		Batsleer2015}}.  \added[id=JJ]{This discarding of fish in
	excess of quota hampers the ability to limit fishing mortality to
	within sustainable limits \citep{Alverson1994, Crowder1998,
		Rijnsdorp2007}} \deleted[id=PD]{; reducing discarding is
	crucial}and the ability to manage for the biological and economic
sustainability of fisheries\deleted[id=JJ]{ and implementation of an ecosystem
	approach to fisheries}. As such, there is increasing interest in
technical solutions such as gear and spatial closures as ways of
\replaced[id=PD]{reducing unwanted catch}{avoiding discard\added[id=JJ]{ing of
		fish}}\citep{Kennelly2002, Catchpole2008, Bellido2011}.  \\

\replaced[id=PD]{Changes to spatial fishing patterns have}{Use of spatial
	management as a tools} been proposed as a method to reduce discards
\added[id=PD]{\citep{Holmes2011, Little2014, Dunn2014a}}. However,
\deleted[id=PD]{its} implementation of avoidance measures is hampered by lack
of knowledge of fish and fishery spatiotemporal dynamics and understanding of
the scale at which processes are important for management. Understanding the
correct scale for spatial measures is crucial in order to implement measures at
a resolution that ensures effective management \citep{Dunn2016} while
minimising economic impact.  For example, a scale that promotes species
avoidance for vulnerable or low quota species while allowing continuance of
sustainable fisheries for available quota species.\\

\replaced[id=PD]{Identifying}{Ensuring measures are implemented at} an
appropriate scale has been a challenge in the past that has led to ineffectual
measures with unintended consequences such as limited impact towards the
management objective or increased benthic impact on previously unexploited
areas (e.g. the cod closure in the North Sea
\citep{Rijnsdorp2001,Dinmore2003}). \replaced[id=PD]{M}{Since then m}ore
refined spatial information has \added[id=PD]{since} become available through
the combination of logbook and Vessel Monitoring System (VMS) data
\citep{Lee2010, Bastardie2010, Gerritsen2012, Mateo2016} and more real-time
spatial management has been possible \citep[e.g.][]{Holmes2011}.  However, such
information is derived from an inherently biased sampling programme, targeted
fishing. \deleted[id=PD]{ Further, fishers generally only recorded landings
	(not catch) on a daily basis\todo{\added[id=JJ]{Its not clear what the
			problem is: landings collected on daily basis or
			landings recorded rather than catch}}.  This leads to
	questions about the validity of inference that can be drawn from
	landings data assigned to VMS activity pings.}\todo{\added[id=JJ]{This
		comes as a surprise: I thought this was going to be about
		discards}\added[id=PD]{Agree, have removed this to avoid
		confusion}}\\

In order to understand \replaced[id=PD]{the consequences of using}{challenges
	that face} VMS-linked landings to draw inference on the underlying
population structure we develop a simulation model where population dynamics
are highly-resolved in space and time\replaced[id=PD]{. Being}{ and are}
known \added[id=PD]{directly} rather than inferred from sampling or commercial
catch\added[id=PD]{, we can use the population model to evaluate how inference from
	fisheries-dependent and fisheries independent sampling relates to the
	real population structure}. \replaced[id=PD]{In our model system
	p}{P}opulation movement is driven by random (diffusive) and directed
(advective) processes and we incorporate characterisation of a number of
different fishing \added[id=PD]{fleet dynamics} exploiting four fish populations
with different spatial and population demographics.\\

Using our model we simulate \replaced[id=PD]{50}{40} years of exploitation of
the fish populations. \replaced[id=PD]{We}{ and} use the
results\deleted[id=PD]{ from the fishing model:}

\begin{enumerate}
	\item to understand how sampling-derived data reflects the underlying
		population structures. We compare at different spatial and
		temporal aggregations of the simulated population distributions
		to: 
		\begin{enumerate}
			\item the inferred population from a stratified
				fixed-site sampling survey design commonly used
				for fisheries monitoring purposes, otherwise
				know as a fisheries-independent survey,
			\item the inferred population from our
				fishery-dependent model which includes
				fishery-induced sampling dynamics.\\
		\end{enumerate}
	\item to understand the impact of data aggregation and data source on
		spatial fisheries management measures we simulate a fishery
		closure to protect a species based on different spatial and
		temporal data aggregations:
		\begin{enumerate}
			\item as if the real spatial population structure were
				known,
			\item the fishery-independent inferred population
				structure
			\item the fishery-dependent inferred population
				structure
		\end{enumerate}
		We evaluate the theoretical "benefit" to the population of the
		closure(s), the effect on the other three populations and
		fishery catch.\todo{\added[id=JJ]{If the paper has two goals
				this should be clear from the start, but may be
				better over 2 MSs}\added[id=PD]{I would like to
				keep both parts, but have made clearer in how
				its set out. The closure scenarios form
				validation of the data aggregation, rather than
				effectiveness of the closures themselves - so
				its a continuation of the same question in my
				eyes}}\deleted[id=PD]{.  Further, we extend our
			analysis to a range of spatial and temporal scales to
			assess the impact of these processes on the success of
			the management measure.}\\
\end{enumerate}

@@

\deleted[id=PD]{The fishing model operated on a tow-by-tow basis, while}
\replaced[id=PD]{P}{p}opulation dynamics (fishing and natural mortality,
growth) operate on a daily time-step\replaced[id=PD]{, while p}{. P}opulation
movement occurs on a weekly time-step\replaced[id=PD]{. R}{, while r}ecruitment
\replaced[id=PD]{takes place}{occurs} periodcally each year for a set time
\replaced[id=PD]{duration}{period (e.g. 3 weeks)} specified for each
population\deleted[id=PD]{.}\added[id=PD]{, while the fishing module operates
	on a tow-by-tow basis (i.e. multiple events a day)}.  The simulation
framework is implemented in the statistical software package R
\citep{RCoreTeam2017} \replaced[id=PD]{and}{;} available as an R package from
the authors github site (\url{www.github.com/pdolder/MixFishSim}).\\

\deleted[id=PD]{Here we describe each of the model components; 1) Population
	dynamics, 2) Recruitment dynamics, 3) Population movement dynamics, 4)
	fishery dynamics.}

@@

The basic population level processes are simulated using a modified two-stage
Deriso-Schnute delay difference model \citep{Deriso1980, Schnute1985,
	Dichmont2003} occurring at a daily time-step. \added[id=PD]{A daily
	time-step was chosen as to discretise continuous population processes
	on a biologically relevant and computationally tractable timescale.}
\replaced[id=PD]{Under the population dynamics module}{Here,} population
biomass growth and depletion for pre-recruits and \deleted[id=PD]{fish}
recruited \added[id=PD]{fish} \deleted[id=PD]{to the fishery} are modelled
separately as a function of previous recruited biomass, intrinsic population
growth and recruitment. Biomass for each cell is incremented each day as
follows (the full parameter list is detailed in Table \ref{tab: pop_variable}):
\begin{equation}
	\begin{split}
	B_{c,d+1} = &\\
	& (1 + \rho) B_{c,d} \cdot e^{-Z_{c,d}} - \rho \cdot e^{-Z_{c,d}} \hspace{2.9cm}
	\times \\  
	& (B_{c,d-1} \cdot e^{-Z_{c,d-1}} + Wt_{R-1} \cdot \alpha_{d-1} \cdot
	R_{\tilde{y}(c,y,d-1)})
	\hspace{0.4cm} + \\
	& Wt_{R} \cdot \alpha_{d} \cdot R_{\tilde{y}(c,y,d)} 
	\end{split}
\end{equation}
where $\rho$ is Brody's coefficient, shown to be approximately equal to
$e^{-K}$ when $K$ is the growth rate from a von Bertalanffy logistic growth
model \citep{Schnute1985}. $Wt_{R-1}$ is the weight of fish prior to
recruitment, while $Wt_{R}$ is the recruited weight. $\alpha_{d}$ represents
the proportion of fish recruited during that day for the year, while
$R_{c,\tilde{y}}$ is the annual recruits in cell $c$ for year $y$. \\

@@

Recruitment is modelled through a function relating the mature biomass to
recruits at time of recruitment. In \emph{MixFishSim}, it can be modelled
either either as a stochastic Beverton-Holt stock-recruit form
\citep{Beverton1957}: 
\begin{equation}
	\begin{split}
	\bar{R}_{c,d} = & \frac{(\alpha * B_{c,d})}{(\beta + B_{c,d})} \\
	     R_{c,d} \sim & \log N[(\log(\bar{R}_{c,d}),\log(\sigma^2))]
	\end{split}
\end{equation}
Where $\alpha$ is the maximum recruitment rate, $\beta$ the spawning stock
biomass (SSB) required to produce half the maximum, $B$ current SSB and
$\sigma^2$ the variability in the recruitment due to stochastic
processes, or a stochastic Ricker form \citep{Ricker1954}:
\begin{equation}
	\begin{split}
	\bar{R}_{c,d} = & B_{c,d} * e^{(\alpha - \beta * B_{c,d})} \\	
   	     R_{c,d} \sim & \log N[(\log(\bar{R}_{c,d}),\log(\sigma^2))]
	\end{split}
\end{equation}
where $\alpha$ is the maximum productivity per spawner and $\beta$ the density
dependent reduction in productivity as the SSB increases. In this study, the
Beverton-Holt form of stock recruit relationship was used for all populations.

@@

\replaced[id=PD]{T}{In the simulation model, t}he habitat for each of the
populations \replaced[id=PD]{was}{is} generated \replaced[id=PD]{with}{through}
the \textit{RFSimulate} function of the \textit{RandomFields} R package
\citep{Schlater2015}. Each population \replaced[id=PD]{was}{is} initialised at
a single location, and subsequently move\replaced[id=PD]{ed}{s} according to a
probabilistic distrib\added[id=PD]{u}tion based on habitat suitability
(represented by the normalised values from the GRFs), temperature and distance
from current cell\replaced[id=PD]{:}{.} 
\begin{equation}
	Pr(J | I) = \frac{e^{-\lambda * d_{IJ}} \cdot
		(Hab_{J,p}^2 \cdot Tol_{J,p,wk})}{\sum\limits_{c=1}^{C}e^{-\lambda * d} \cdot
		(Hab_{c,p}^2 \cdot Tol_{c,p,wk})}
\end{equation}
Where $d_{IJ}$ is the euclidean distance between cell $I$ and cell $J$,
$\lambda$ is a given rate of decay, $Hab_{J,p}^2$ is the squared index of
habitat suitability for cell $J$ and population $p$, with $Tol_{J,p,wk}$ the
temperature tolerance for cell $J$ by population $p$ in week $wk$.\\

@@

Where several fishing vessels are exploiting the same fish population
competition is known to play an important role in local distribution of fishing
effort \citep{Gillis1998}. If several vessels are fishing on the same patch of
fish, local depletion and interference \added[id=JJ]{competition} will affect
fishing location choice of the fleet as a whole \citep{Rijnsdorp2000,
	Poos2007a}. In order to account for this behaviour, the fishing
sub-model operates spatially on a daily time-step so that for future days the
biomass available to the fishery is reduced in the areas fished. The cumulative
effect is to make heavily fished areas less attractive as future fishing
opportunities.

@@

A fisheries-independent survey is simulated where fishing on a regular grid
begins each year at the same time for a given number of stations (a fixed
station survey design). Catches of the populations \replaced[id=JJ]{at each
station}{present} are recorded but not removed from the population. This
provides a fishery independent snapshot of the populations at a regular spatial
\replaced[id=JJ]{intervals}{distribution} each year, similar to scientific
surveys undertaken by fisheries research agencies.

\section{Calculation}

@@

The fleets were parametrised to reflect five different characteristic fisheries
with unique exploitation dynamics (Table \ref{tab:2}).  \replaced[id=PD]{By
	setting different catchability parameters ($Q_{fl, p}$) we create
	different targeting preferences between the fleets and hence spatial
	dynamics}{This ensures that different fleets have different spatial
	dynamics, preferentially targeted different fish populations}.  The
stochasticity in the random walk process ensures that within a fleet different
vessels have slightly different spatial distributions based on individual
experience. The step function was parametrised dynamically within the
simulations as the maximum revenue obtainable was not known beforehand. This
was implemented so that vessels take smaller steps when fishing at a location
yields landings value which is in the top 90th percentile of the value
experienced in that year (as defined per fleet in Table \ref{tab:2}). \\

With increasing probability throughout the simulation, fishing locations were
chosen based on experience of profitable catches built up in the same month
from previous years and from the previous trip. 'Profitable' in this context
was defined as the locations where the top 70 \% of expected profit would be
found given previous trips revenue and cost of movement to the new fishing
location.  This probability was based on a logistic sigmoid function with a
lower asymptote of 0 and upper asymptote of 0.95, and a growth rate which
ensures the upper asymptote (where decisions are mainly based on past
knowledge) is reached $\sim$ halfway through the simulation.  \\

@@

\subsection{Simulation settings}

To illustrate the capabilities on \emph{MixFishSim}, we investigate the
influence of the temporal and spatial resolution of different data sources on
the reduction in catches of a population given spatial closures. To do so, we
set up a simulation to run for 50 years based on a 100 $\times$ 100 square
grid, with five fleets of 20 vessels each and four fish populations. Fishing
takes place four times a day per vessel and five days a week, while population
movement is every week.\todo{\added[id=JJ]{move to start of methods
		section}\added[id=PD]{I think ecological modelling wants the
		'calculations' section here..will check}} \\

@@

\begin{itemize}
	\item \textbf{data types:} commercial logbook data, survey data and
		'real population',
	\item \textbf{temporal resolutions:} weekly, monthly and yearly
		closures,
	\item \textbf{spatial resolutions:} 1 x 1 grid, 5 x 5 grid, 10 x 10
		grid and 20 x 20 grid,
	\item \textbf{closure basis:} high catch rates of protected species, or
		high ratio of protected species v secondary species.
\end{itemize}

@@

@@

The finer spatial grid for the real population (top left) and commercial data
(top middle) show visually similar patterns, though there are large unsampled
areas in the commercial data from a lack of fishing activity (particularly in
the lower left part of the sampling domain). The survey data at this spatial
resolution shows very sparse information about the spatial distributions of the
populations. The slightly aggregated data on a 5 x 5 grid shows similar
patterns and, while losing some of the spatial detail, there remains good
consistency between the 'real population' and the commercial data. Survey data
starts to pick out some of the similar patterns as the other data sources, but
lacks coverage. The spatial catch information on a 10 x 10 and 20 x 20 grid
loses a significant amount of information about the spatial resolutions for all
data sources, and some differences between the survey, commercial and 'real
population' data emerge. \\

@@

As can be seen by comparison to the 'real population', the monthly aggregation
captures the major patterns seen in the weekly data, albeit missing more subtle
differences. The yearly data results in a constant catch pattern due to the
aggregation process (sometimes known as an aggregation bias). The commercial
data on a weekly basis shows some of the same patterns as the 'real
population', though the first species (in red) is less well represented and
some weeks are missing catches from the area. The monthly data. The monthly
data shows some consistency between the 'real population' and commercial data
for species 2 - 4, though species 1 remains under-represented. On an annual
basis, interestingly the commercial data under represents the first species (in
red) while the survey over represents species 1. This is likely due to the
biases in commercial sampling, with the fisheries not targeting the areas where
species 1 are present, and the biases in the survey sampling from over
representation of the spatial distribution. \\

@@

For the closures based on 'real population' (bottom row), the most
disaggregated data (a weekly timescale and 1 x 1 resolution) was most
effective, reducing fishing mortality on species 1 (left) by $\sim$ 60 \%. Next
was the monthly closures ($<$ $\sim$ 30 \%).  The least effective were the
yearly closures (blue lines) at all spatial resolutions, which resulted in
increased fishing mortalities ($>$ 30 \%). \\

@@

For the commercial data, the most effective closure scenario was based on 1 x 1
data at a monthly temporal resolution. This results in $\sim$ 10 \% reduction
in F for species 1. \textcolor{blue}{This was the only closure scenario to have
	positive effect according to Figure \ref{fig:4}, though looking at the
	trend in Figure \ref{fig:3} this looks more related to the continued
	increased in F trend, as other scenarios had an initial effect}.
Interestingly the monthly data scenario was more effective than weekly data,
which I'd posit is due to the increase amount of data available from the
commercial sampling across a month compared to a week. Commercial data used at
an annual time-step was ineffective in bringing fishing mortality down for
species 1. \\

>>>>

\usepackage{enumitem}

@@

We simulate 50 years of fishing and use the results from the fisheries catch to
draw inference on the underlying population structures. We compare this
inference to a simulated fixed-site sampling design commonly used for fisheries
monitoring purposes and the true underlying population structures input to the
simulation. We i) use the results to establish the potential and limitations of
fishery-dependent data in providing a robust picture of spatiotemporal
distributions; and ii) simulate an area closure based on areas defined from the
different data sources at a range of temporal and spatial resolutions and
assess their effectiveness on reducing catches of a fish population. \\

@@

Fishers exploit a variety of fish populations that are heterogeneously
distributed in space and time with varying knowledge of species distributions
using species non-selective fishing gear. \added[id=PD]{In doing so} fisheries
\deleted[id=PD]{that}catch an assemblage of species
\added[id=PD]{and}\deleted{, known as mixed fisheries} \replaced[id=JJ]{may}{,
	when managed by single-species quotas can end up}
discard\deleted[id=JJ]{ing} over-quota catch \added[id=JJ]{when managed by
	single species quotas and fishers exhaust one or more quota which may}
lead to overexploitation of fish populations \added[id=JJ]{\citep{Ulrich2011a,
		Batsleer2015}}.  \added[id=JJ]{This discarding of fish in
	excess of quota limits the ability to maintain fishing mortality within
	sustainable limits \citep{Alverson1994, Crowder1998, Rijnsdorp2007}}
\deleted[id=PD]{; reducing discarding is crucial}and the ability to manage for
the biological and economic sustainability of fisheries\deleted[id=JJ]{ and
	implementation of an ecosystem approach to fisheries}. As such, there
is increasing interest in technical solutions such as gear and spatial closures
as measures to \replaced[id=PD]{reduce unwanted catch}{avoiding
	discard\added[id=JJ]{ing of fish}}\citep{Kennelly2002, Catchpole2008,
	Bellido2011}.  \\

\replaced[id=PD]{Changes to spatial fishing patterns have}{Use of spatial
	management as a tools} been proposed as a method to reduce discards
\added[id=PD]{\citep{Holmes2011, Little2014, Dunn2014a}}.  \deleted[id=PD]{its}
implementation of avoidance measures is, however, restricted by lack of
knowledge of fish and fishery spatiotemporal dynamics and understanding of the
scale at which processes become important for management. Understanding the
correct scale for spatial measures is crucial for implementation at a
resolution that ensures effective management \citep{Dunn2016} while minimising
economic impact.  For example, a scale that promotes species avoidance for
vulnerable or low quota species while allowing continuance of sustainable
fisheries for available quota species.\\

\replaced[id=PD]{Identifying}{Ensuring measures are implemented at} an
appropriate scale has been a challenge in the past that has led to ineffectual
measures with unintended consequences such as limited impact towards the
management objective or increased benthic impact on previously unexploited
areas (e.g. the cod closure in the North Sea
\citep{Rijnsdorp2001,Dinmore2003}). \replaced[id=PD]{M}{Since then m}ore
refined spatial information has \added[id=PD]{since} become available through
the combination of logbook and Vessel Monitoring System (VMS) data
\citep{Lee2010, Bastardie2010, Gerritsen2012, Mateo2016} and more real-time
spatial management has been possible \citep[e.g.][]{Holmes2011}.  Such
information is, however, derived from an inherently biased sampling programme,
targeted fishing. \deleted[id=PD]{ Further, fishers generally only recorded
	landings (not catch) on a daily basis\todo{\added[id=JJ]{Its not clear
			what the problem is: landings collected on daily basis
			or landings recorded rather than catch}}.  This leads
	to questions about the validity of inference that can be drawn from
	landings data assigned to VMS activity pings.}\todo{\added[id=JJ]{This
		comes as a surprise: I thought this was going to be about
		discards}\added[id=PD]{Agree, have removed this to avoid
		confusion}}\\

\replaced[id=PD]{We ask two fundamental questions regarding spatiotemporal
	inference derived from observational data:}{ and use the
	results}\deleted[id=PD]{ from the fishing model:}

\begin{enumerate}
	\item How does sampling-derived data reflects the underlying population
		structures? 	
	\item How does data aggregation and source impact on monitoring spatial
		fisheries management measures ? \end{enumerate}

We i) develop a simulation model where population dynamics are highly-resolved
in space and time to answer these questions\replaced[id=PD]{. Being}{ and are}
known \added[id=PD]{directly} rather than inferred from sampling or commercial
catch\added[id=PD]{, we can use the population model to evaluate how inference
	from fisheries-dependent and fisheries independent sampling relates to
	the real population structure}. We ii) compare at different spatial and
temporal aggregations of the simulated population distributions to samples from
fisheries-dependent and fisheries independent catches. We then iii) simulate a
fishery closure to protect a species based on different spatial and temporal
data aggregations. \\

We compare the catch composition from fisheries independent and dependent
sampling against the real population composition, as well as the theoretical
"benefit" to the population spatial closures using the different data sources.
We use these evaluations to draw inference on the utility of commercial data in
supporting management decisions. \todo{\added[id=JJ]{If the paper has two goals
		this should be clear from the start, but may be better over 2
		MSs}\added[id=PD]{I would like to keep both parts, but have
		made clearer in how its set out.  The closure scenarios form
		validation of the data aggregation, rather than effectiveness
		of the closures themselves - so its a continuation of the same
		question in my eyes}}\deleted[id=PD]{.  Further, we extend our
	analysis to a range of spatial and temporal scales to assess the impact
	of these processes on the success of the management measure.}\\

@@

\deleted[id=PD]{The fishing model operated on a tow-by-tow basis, while}
\replaced[id=PD]{P}{p}opulation dynamics (fishing and natural mortality,
growth) operate on a daily time-step\replaced[id=PD]{, while p}{. P}opulation
movement occurs on a weekly time-step\replaced[id=PD]{. R}{, while r}ecruitment
\replaced[id=PD]{takes place}{occurs} periodically each year for a set time
\replaced[id=PD]{duration}{period (e.g. 3 weeks)} specified for each
population\deleted[id=PD]{.}\added[id=PD]{, while the fishing module operates
	on a tow-by-tow basis (i.e. multiple events a day)}.  
\deleted[id=PD]{Here we describe each of the model components; 1) Population
	dynamics, 2) Recruitment dynamics, 3) Population movement dynamics, 4)
	fishery dynamics.}

\replaced[id=PD]{In our model system p}{P}opulation movement is driven by
random (diffusive) and directed (advective) processes and we incorporate
characterisation of a number of different fishing \added[id=PD]{fleet dynamics}
exploiting four fish populations with different spatial and population
demographics. We use the model to simulate \replaced[id=PD]{50}{40} years of
exploitation of the fish populations.

@@

The basic population level processes are simulated using a modified two-stage
Deriso-Schnute delay difference model \citep{Deriso1980, Schnute1985,
	Dichmont2003} occurring at a daily time-step. \added[id=PD]{A daily
	time-step was chosen to discretise continuous population processes
	on a biologically relevant and computationally tractable timescale.}
\replaced[id=PD]{Under the population dynamics module}{Here,} population
biomass growth and depletion for pre-recruits and \deleted[id=PD]{fish}
recruited \added[id=PD]{fish} \deleted[id=PD]{to the fishery} are modelled
separately as a function of previous recruited biomass, intrinsic population
growth and recruitment. Biomass for each cell $c$ is incremented each day $d$ as
follows (the full parameter list is detailed in Table \ref{tab: pop_variable}):
\begin{equation}
	\begin{split}
	B_{c,d+1} = &\\
	& (1 + \rho) B_{c,d} \cdot e^{-Z_{c,d}} - \rho \cdot e^{-Z_{c,d}} \hspace{2.9cm}
	\times \\  
	& (B_{c,d-1} \cdot e^{-Z_{c,d-1}} + Wt_{R-1} \cdot \alpha_{d-1} \cdot
	R_{\tilde{y}(c,y,d-1)})
	\hspace{0.4cm} + \\
	& Wt_{R} \cdot \alpha_{d} \cdot R_{\tilde{y}(c,y,d)} 
	\end{split}
\end{equation}
where $\rho$ is Brody's coefficient, shown to be approximately equal to
$e^{-K}$ when $K$ is the growth rate from a von Bertalanffy logistic growth
model \citep{Schnute1985}. $Wt_{R-1}$ is the average weight of fish prior to
recruitment, while $Wt_{R}$ is the average recruited weight. $\alpha_{d}$
represents the proportion of fish recruited during that day for the year, while
$R_{c,\tilde{y}}$ is the annual recruits in cell $c$ for year $y$. \\

@@

Recruitment is modelled through a function relating the mature biomass to
recruits at time of recruitment. In \emph{MixFishSim}, it can be modelled
either either as a stochastic Beverton-Holt stock-recruit form
\citep{Beverton1957}: 
\begin{equation}
	\begin{split}
	\bar{R}_{c,d} = & \frac{(\alpha * S_{c,d})}{(\beta + S_{c,d})} \\
	     R_{c,d} \sim & \log N[(\log(\bar{R}_{c,d}),\sigma^2)]
	\end{split}
\end{equation}
Where $\alpha$ is the maximum recruitment rate, $\beta$ the spawning stock
biomass (SSB) required to produce half the maximum stock size, $S$ current
stock size and $\sigma^2$ the variability in the recruitment due to stochastic
processes, or a stochastic Ricker form \citep{Ricker1954}:
\begin{equation}
	\begin{split}
	\bar{R}_{c,d} = & B_{c,d} * e^{(\alpha - \beta * B_{c,d})} \\	
   	     R_{c,d} \sim & \log N[(\log(\bar{R}_{c,d}),\log(\sigma^2))]
	\end{split}
\end{equation}
where $\alpha$ is the maximum productivity per spawner and $\beta$ the density
dependent reduction in productivity as the SSB increases. In this study, the
Beverton-Holt form of stock recruit relationship was used for all populations.

@@

\replaced[id=PD]{T}{In the simulation model, t}he habitat for each of the
populations \replaced[id=PD]{was}{is} generated \replaced[id=PD]{with}{through}
the \textit{RFSimulate} function of the \textit{RandomFields} R package
\citep{Schlater2015}. Each population \replaced[id=PD]{was}{is} initialised at
a single location, and subsequently move\replaced[id=PD]{ed}{s} according to a
probabilistic distrib\added[id=PD]{u}tion based on habitat suitability
(represented by the normalised values from the GRFs), temperature and distance
from current cell\replaced[id=PD]{:}{.} 
\begin{equation}
	Pr(J | I) = \frac{e^{-\lambda * d_{IJ}} \cdot
		(Hab_{J,p}^2 \cdot Tol_{J,p,wk})}{\sum\limits_{c=1}^{C}e^{-\lambda * d} \cdot
		(Hab_{c,p}^2 \cdot Tol_{c,p,wk})}
\end{equation}
Where $d_{IJ}$ is the euclidean distance between cell $I$ and cell $J$,
$\lambda$ is a given rate of decay, $Hab_{J,p}^2$ is the squared index of
habitat suitability for cell $J$ and population $p$, with $Tol_{J,p,wk}$ the
temperature tolerance for cell $J$ by population $p$ in week $wk$ (see
below).\\

@@

Where several fishing vessels exploit the same fish population competition is
known to play an important role in local distribution of fishing effort
\citep{Gillis1998}. If several vessels are fishing on the same patch of fish,
local depletion and interference \added[id=JJ]{competition} will affect fishing
location choice of the fleet as a whole \citep{Rijnsdorp2000, Poos2007a}. In
order to account for this behaviour, the fishing sub-model operates spatially
on a daily time-step so that for future days the biomass available to the
fishery is reduced in the areas fished. The cumulative effect is to make
heavily fished areas less attractive as future fishing opportunities.

@@

A fisheries-independent survey is simulated where fishing on a regular grid
begins each year at the same time for a given number of stations (a fixed
station survey design). Catches of the populations \replaced[id=JJ]{at each
station}{present} are recorded but not removed from the population. This
provides a fishery independent snapshot of the populations at a regular spatial
\replaced[id=JJ]{intervals}{distribution} each year, similar to scientific
surveys undertaken by fisheries research agencies. \\

\subsection{Software}

The simulation framework is implemented in the statistical software package R
\citep{RCoreTeam2017} \replaced[id=PD]{and}{;} available as an R package from
the authors github site (\url{www.github.com/pdolder/MixFishSim}).\\

\section{Calculation - used by journal / Parameterisation}

@@

The fleets were parametrised to reflect five different characteristic fisheries
with unique exploitation dynamics (Table \ref{tab:2}).  \replaced[id=PD]{By
	setting different catchability parameters ($Q_{fl, p}$) we create
	different targeting preferences between the fleets and hence spatial
	dynamics}{This ensures that different fleets have different spatial
	dynamics, preferentially targeted different fish populations}.  The
stochasticity in the random walk process ensures that within a fleet different
vessels have slightly different spatial distributions based on individual
experience. The step function was parametrised dynamically within the
simulations as the maximum revenue obtainable was not known beforehand. This
was implemented so that vessels take smaller steps when fishing at a location
that yields landings value in the top 90th percentile of the value experienced
in that year so far (as defined per fleet in Table \ref{tab:2}). \\

With increasing probability throughout the simulation, fishing locations were
chosen based on experience of profitable catches built up in the same month
from previous years and from the previous trip. 'Profitable' in this context
was defined as the locations where the top 70 \% of expected profit would be
found given previous trips revenue and cost of movement to the new fishing
location.  This probability was based on a logistic sigmoid function with a
lower asymptote of 0 and upper asymptote of 0.95, and a growth rate which
ensures the upper asymptote (where decisions are mainly based on past
knowledge) is reached approximately halfway through the simulation.  \\

@@

\subsection{Example research question scenario}

To illustrate the capabilities on \emph{MixFishSim}, we investigate the
influence of the temporal and spatial resolution of different data sources on
the reduction in catches of a population given spatial closures. To do so, we
set up a simulation to run for 50 years based on a 100 $\times$ 100 square grid
(undetermined units), with five fleets of 20 vessels each and four fish
populations. Fishing takes place four times a day per vessel and five days a
week, while population movement is every week.\todo{\added[id=JJ]{move to start
		of methods section}\added[id=PD]{I think ecological modelling
		wants the 'calculations' section here..will check}} \\

@@

\begin{itemize}
	\item \textbf{data types:} commercial logbook data, survey data and
		`real population',
	\item \textbf{temporal resolutions:} weekly, monthly and yearly
		closures,
	\item \textbf{spatial resolutions:} 1 x 1 grid, 5 x 5 grid, 10 x 10
		grid and 20 x 20 grid,
	\item \textbf{closure basis:} high catch rates of protected species, or
		high ratio of protected species v secondary species.
\end{itemize}

@@

In order to answer the question of how sampling-derived data reflects the
underlying population structure we compare different spatial and temporal
aggregations of the simulated population distributions to:
\begin{enumerate}[label=\alph*)]
	\item \textbf{fisheries-independent data:} the inferred population from
		a fixed-site sampling survey design as commonly used for
		fisheries monitoring purposes;
	\item \textbf{fisheries-dependent data:} the inferred population from
		our fleet model which includes fishery-induced sampling
		dynamics.
\end{enumerate}

@@

The finer spatial grid for the real population (top left) and commercial data
(top middle) show visually similar patterns, though there are large unsampled
areas in the commercial data from a lack of fishing activity (particularly in
the lower left part of the sampling domain). The survey data at this spatial
resolution displays very sparse information about the spatial distributions of the
populations. The slightly aggregated data on a 5 x 5 grid shows similar
patterns and, while losing some of the spatial detail, there remains good
consistency between the `real population' and the commercial data. Survey data
starts to pick out some of the similar patterns as the other data sources, but
lacks coverage. The spatial catch information on a 10 x 10 and 20 x 20 grid
lose a significant amount of information about the spatial resolutions for all
data sources, and some differences between the survey, commercial and 'real
population' data emerge. \\

@@

As can be seen by comparison to the 'real population', the monthly aggregation
captures the major patterns seen in the weekly data, albeit missing more subtle
differences. The yearly data results in a constant catch pattern due to the
aggregation process (sometimes known as an aggregation bias). The commercial
data on a weekly basis shows some of the same patterns as the 'real
population', though the first species (in red) is less well represented and
some weeks are missing catches from the area. The monthly data shows some
consistency between the 'real population' and commercial data for species 2 -
4, though species 1 remains under-represented. On an annual basis,
interestingly the commercial data under represents the first species (in red)
while the survey over represents species 1. This is likely due to the
biases in commercial sampling, with the fisheries not targeting the areas where
species 1 are present, and the biases in the survey sampling from over
representation of the spatial distribution. \\

@@

For the closures based on 'real population' (bottom row), the most
disaggregated data (a weekly timescale and 1 x 1 resolution) was most
effective, reducing fishing mortality on species 1 (left) by $\sim$ 60 \%. Next
was the monthly closures ($<$ $\sim$ 30 \%).  The least effective were the
yearly closures (blue lines) at all spatial resolutions, which conversely
resulted in increased fishing mortalities ($>$ 30 \%). \\

@@

For the commercial data, the most effective closure scenario was based on 1 x 1
data at a monthly temporal resolution. This results in $\sim$ 10 \% reduction
in F for species 1. \textcolor{blue}{This was the only closure scenario to have
	positive effect according to Figure \ref{fig:4}, though looking at the
	trend in Figure \ref{fig:3} this looks more related to the continued
	increased in F trend, as other scenarios had an initial effect}.
Interestingly the monthly data scenario was more effective than weekly data,
which we posit is due to the increased data available from the commercial
sampling across a month compared to a week. Commercial data used at an annual
time-step was ineffective in bringing fishing mortality down for species 1. \\
